D3692R1: How to Avoid OOTA Without Really Trying

### 2025-07-08 paper/ootavacuous.tex
ootavacuous: Add reordering of non-volatile atomics on different objects
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Sensible though this recommendation might be, it can unnecessarily raise
anxiety levels of C++ implementers.
After all, what exactly do they need to do in order to follow that
recommendation?
We therefore advocate adding the following non-normative sentence to this
recommendation:
\begin{quote}
	Compiler-based implementations whose binaries run on conventional
	hardware are guaranteed not to compute out-of-thin-air values in
	programs that are free of undefined behavior,
	as long as they restrict themselves to thread-at-a-time analysis
	and do not invent, duplicate, or repurpose atomic accesses.
\end{quote}

>>>>

Sensible though this recommendation might be, it can unnecessarily raise
anxiety levels of C++ implementers.
After all, what exactly do they need to do in order to follow that
recommendation?
We therefore advocate adding the following non-normative sentence to this
recommendation:
\begin{quote}
	Compiler-based implementations whose binaries run on conventional
	hardware are guaranteed not to compute out-of-thin-air values in
	programs that are free of undefined behavior,
	as long as they restrict themselves to thread-at-a-time analysis
	and and treat non-volatile atomic accesses as if they were
	volatile, except that, when permitted by the as-if rule, they
	may omit accesses, merge accesses to the same object, or reorder
	accesses to different objects.
\end{quote}
